Laplacian envelope

### 2020-11-02 Notes/laplace.tex
num_synapse parameter for plots

The flux will be maximised if potentiation is guaranteed to take it to a \(+\) state and depression is guaranteed to take it to a \(-\) state:
%
\begin{equation*}
  \sum_{j \in +} \MMd \pot_{ij} = 1 \quad \forall\, i \in -,
  \qquad
  \sum_{j \in -} \MMd \dep_{ij} = 1 \quad \forall\, i \in +.
\end{equation*}
%
This implies that the process is lumpable to a two state system (see \cite{kemeny1960finite,Ball1993Lumpability,burke1958markovian}):
%
\begin{multline}\label{eq:binarylump}
%\begin{aligned}
  \MMd \pot = \begin{pmatrix}
                0 & 1 \\
                0 & 1 \\
              \end{pmatrix}
  ,\quad
  \MMd \dep = \begin{pmatrix}
                1 & 0 \\
                1 & 0 \\
              \end{pmatrix}
  ,\quad
  \w = \begin{pmatrix}
           -1 \\
           1 \\
         \end{pmatrix}
  ,\\ \implies\quad
  \frg = \begin{pmatrix}
           -f\pot & f\pot \\
           f\dep & -f\dep \\
         \end{pmatrix}
  ,\quad
  \eq = \begin{pmatrix}
           f\dep & f\pot \\
         \end{pmatrix}
  ,
\end{multline}s
%
which leads to the initial SNR
\footnote{Note that including the dropped factors in \cref{eq:SNRcurveExact} would only change this to
\(\SNR(0) \leq \frac{\sqrt{N} (4f^+f^-)}{\sqrt{1 - (f\pot - f\dep)^4}}\),
which is also maximised at \(f\potdep = \frac{1}{2}\) and would therefore have no effect on what follows.}
%
\begin{equation}\label{eq:binarySNR}
  \SNR(0) \leq \sqrt{N} (4 f\pot f\dep) .
\end{equation}
%
This is maximised at \(f\pot = f\dep = \frac{1}{2}\),
leading to the inequality firt shown in \cite{Lahiri2013synapse}:
%
\begin{equation}\label{eq:initbnd}
  \snr(0) \leq \sqrt{N},
\end{equation}
%
The model that saturates this bound is (equivalent to) a two-state model with deterministic transitions and \(f\potdep=\frac{1}{2}\).

>>>>

The flux will be maximised if potentiation is guaranteed to take it to a \(+\) state and depression is guaranteed to take it to a \(-\) state:
%
\begin{equation*}
  \sum_{j \in +} \MMd \pot_{ij} = 1 \quad \forall\, i \in -,
  \qquad
  \sum_{j \in -} \MMd \dep_{ij} = 1 \quad \forall\, i \in +.
\end{equation*}
%
This implies that the process is lumpable to a two state system (see \cite{kemeny1960finite,Ball1993Lumpability,burke1958markovian}):
%
\begin{multline}\label{eq:binarylump}
%\begin{aligned}
  \MMd \pot = \begin{pmatrix}
                0 & 1 \\
                0 & 1 \\
              \end{pmatrix}
  ,\quad
  \MMd \dep = \begin{pmatrix}
                1 & 0 \\
                1 & 0 \\
              \end{pmatrix}
  ,\quad
  \w = \begin{pmatrix}
           -1 \\
           1 \\
         \end{pmatrix}
  ,\\ \implies\quad
  \frg = \begin{pmatrix}
           -f\pot & f\pot \\
           f\dep & -f\dep \\
         \end{pmatrix}
  ,\quad
  \eq = \begin{pmatrix}
           f\dep & f\pot \\
         \end{pmatrix}
  ,
\end{multline}s
%
which leads to the initial SNR%
\footnote{Note that including the dropped factors in \cref{eq:SNRcurveExact} would only change this to
\(\SNR(0) \leq \frac{\sqrt{N} (4f^+f^-)}{\sqrt{1 - (f\pot - f\dep)^4}}\),
which is also maximised at \(f\potdep = \frac{1}{2}\) and would therefore have no effect on what follows.}
%
\begin{equation}\label{eq:binarySNR}
  \SNR(0) \leq \sqrt{N} (4 f\pot f\dep) .
\end{equation}
%
This is maximised at \(f\pot = f\dep = \frac{1}{2}\),
leading to the inequality (first shown in \cite{Lahiri2013synapse}):
%
\begin{equation}\label{eq:initbnd}
  \snr(0) \leq \sqrt{N},
\end{equation}
%
The model that saturates this bound is (equivalent to) a two-state model with deterministic transitions and \(f\potdep=\frac{1}{2}\).
